---
title: 'Assignment #4: Summary of your final project'
author: "Taufiq Ahmad"
date: "2024-11-22"
output: html_document
---

## Framing Artificial Intelligence in Disaster Management: Analyzing U.S.                                Organizational Press Releases


#Project Overview:

This project investigates how U.S. organizations frame AI in press releases concerning disaster response and management. More specifically, I would focus on how  AI is framed in organizational press releases related to disaster management, what are key themes and dominant narratives related the discussions of AI in the context of natural disasters and crises in United States and finally what potential risks and ethical concerns regarding AI usage are highlighted in these communications?


#Objective of the Project: 
 
Analyze how U.S. organizations frame AI in press releases during disaster response and management efforts.      

## RQs

  1. How is AI framed in organizational press releases related to disaster?
  2. What are the dominant themes associated with AI in the context of disaster?
  3. What are the risks and ethical concerns regarding AI in the context of disaster?
  

## Data collection

Data has been collected from the database Nexis Uni, focusing on press releases disseminated through major news wires. The collection period spans from July 1, 2024, to December 1, 2024, using the keywords "Artificial Intelligence" OR "AI" AND "disaster". The final dataset comprises 500 press releases sourced mainly from the following news wires:

  1. States News Service
  2. Targeted News Service
  3. PR Newswire
  4. Business Wire
  5. GlobeNewswire

These press releases explicitly mention "Artificial Intelligence" or "AI" in conjunction with disasters.


## A Quick Overview of the data 

Total Press Releases: 500
Time Period Covered: July 1, 2024 – December 1, 2024
Average Releases Per Month: 110
Top Mentioned Keywords: "Artificial Intelligence," "AI," "Disaster"

Dominant Headlines of the Press Releases:
  Ethical Concerns
  Public Trust
  AI Benefits
  AI Limitations

Regional Focus: United States

Organizations Highlighted:
  FEMA
  Department of Homeland Security
  Major Tech Companies
  Non-Governmental Organizations (NGOs)


## Data Analysis Approach 

A computational textual analysis approach is employed to analyze the collected press releases. The analysis is conducted using R programming, leveraging various libraries and packages to facilitate data processing and analysis. The key steps include:

Data Cleaning and Preparation:

  1. Content Analysis:
  2. Sentimental Analysis:
  3. Topic Modeling & Thematic Analyis:
  4. Visualization and Reporting:

Expected Outcomes

  1. Comprehensive Understanding
  2. Theme Identification
  3. Ethical Insights
  4. Strategic Recommendations
  
##Repository Highlights

  1. GitHub Repository: FramingAI
  2. Data Access: FramingAI Data Repository
  3. Codebook Structure
  4. Data Samples
  5. Descriptive Statistics
  6. Analytical Tools

## Appropriate libraries

```{r echo= T, results = 'hide', warning=F, error=F, message=F}
library(tidyverse)
library(pdftools)
library(tidyverse)
library(textdata)
library(tidytext)
library(quanteda)
library(rio)
library(janitor)
library(rio)
library(dplyr)
library(stringr)
library(readr)
here::here()
#topic modeling
library(tm)
library(topicmodels)
library(lda)
library(ldatuning)
# from tutorial packages
library(DT)
library(knitr) 
library(kableExtra) 
library(reshape2)
library(ggplot2)
library(wordcloud)
library(pals)
library(SnowballC)
library(flextable)
```

## loading the Data
#Here I am starting with uploading PDF data, reading the files, converting theim into text and them combining the text, and spliting into the documents. 

```{r}
#reading PDF file and converting it into text. 
text <- pdf_text("../data/FramingAI.PDF")
writeLines(text, "../data/FramingAI.text")
file_path <- "../data/FramingAI.text"
text_data <- readLines(file_path)
text_combined <- paste(text_data, collapse = "\n")
documents <- strsplit(text_combined, "End of Document")[[1]]
output_dir <- "../data/extracted"
for (i in seq_along(documents)) {
  output_file <- file.path(output_dir, paste0("FramingAI_extracted", i, ".txt"))
  writeLines(documents[[i]], output_file) 
}
cat("Files created:", length(documents), "\n")

FramingAI_index <- read_lines("../data/extracted/FramingAI_extracted1.txt")
extracted_lines <-FramingAI_index[20:2360]
cat(head(extracted_lines, 20), sep = "\n")
extracted_lines <- extracted_lines |> 
  as.data.frame() 
```

## Build a final dataframe index

```{r}

cleaned_data <- extracted_lines |>
  mutate(
    trimmed_line = str_trim(extracted_lines),  
    is_title = str_detect(trimmed_line, "^\\d+\\. "),  

    # Detect dates (e.g., "Aug 14, 2024")
    is_date = str_detect(trimmed_line, "\\b\\w{3} \\d{1,2}, \\d{4}\\b")
  )

# Shifting dates to align with corresponding titles
aligned_data <- cleaned_data |>
  mutate(
    date = ifelse(lead(is_date, 1), lead(trimmed_line, 1), NA_character_)  # Shift date to title's row
  ) |>
  filter(is_title) |>
  select(trimmed_line, date)  # Keep only the relevant columns

# Step 3: Rename columns for clarity
final_data <- aligned_data |>
  rename(
    title = trimmed_line,
    date = date
  )

# Date and Publication in separate columns, and formatted
final_data <- separate(data = final_data, col = date, into = c("date2", "publication"), sep = "  ", extra = "merge", fill = "right")


#Step 5: Format date, clean headline
final_data <- final_data |> 
  mutate(date = as.Date(date2,format = "%b %d, %Y")) |> 
  mutate(title =str_remove(title, "^\\d+\\. ")) |> 
  subset(select = -(date2)) |> 
  mutate(index = row_number()) |> 
  select(index, date, title, publication)

write_csv(final_data, "./final_data.csv")
```

## Raw text compiler 
###creating an index with the file path to the stories and then compiling the stories into a dataframe. 

```{r include=FALSE}

files <- list.files("../data/extracted", pattern="*.txt") %>% 
  as.data.frame() |> 
  rename(filename = 1) |> 
  
  #create an index with the file name
 mutate(index = str_extract(filename, "\\d+")) |> 
  mutate(index = as.numeric(index))


#Join the file list to the index

final_index <- final_data |> 
  inner_join(files, c("index")) |> 
mutate(filepath = paste0("../data/extracted/", filename))

#Display the head of the complied dataframe with filenaems and content 
head(final_index)
```

## Text compiler

```{r echo= T, results = 'hide', warning=F, error=F, message=F}

# Define function to loop through each text file 

create_article_text <- function(row_value) {
  temp <- final_index %>%
    slice(row_value)
  
 
  temp_filename <- temp$filename
  
  articles_df_temp <- read_lines(temp$filepath) %>%
    as_tibble() %>%
    mutate(filename = temp_filename)
 
  articles_df <<- articles_df %>%
    bind_rows(articles_df_temp)
}

articles_df <- tibble()
row_values <- 1:nrow(final_index)

lapply(row_values, create_article_text)


# Clean up articles_df and join to index dataframe
articles_df <- articles_df %>%
  select(filename, sentence=value) %>%
  inner_join(final_index)

#After viewing articles_df, I see 2022 lines from the index that I don't need. Cutting them 

articles_df <- articles_df %>%
  slice(-c(1:2022)) |> 
  #gets rid of blank rows
    filter(trimws(sentence) != "") 

write_csv(articles_df, "./articles_df.csv")
```

## Bigrams

```{r include=FALSE}
# Load required libraries
library(dplyr)
library(stringr)
library(tidytext)

bigrams <- articles_df %>% 
  select(sentence) %>% 
  mutate(
    sentence = str_squish(sentence),                      # Remove extra spaces
    sentence = tolower(sentence),
    sentence = str_replace_all(sentence, c(
    "copyright" = "",
    "new york times"="",
    "publication"="",
    "www.alt"="",
    "http"=""))) %>% 
  unnest_tokens(bigram, sentence, token = "ngrams", n = 2) %>% 
  separate(bigram, c("word1", "word2"), sep = " ") %>% 
  filter(!word1 %in% stop_words$word) %>%                 # Filter out stop words
  filter(!word2 %in% stop_words$word) %>% 
  count(word1, word2, sort = TRUE) %>% 
  filter(!is.na(word1) & !is.na(word2))   
    
# Ensure `stop_words` data is available
data("stop_words")

# Define the pattern to remove specific unwanted terms
remove_pattern <- paste(
  "title|pages|publication date|publication subject|publication type|issn|language of publication: english|",
  "document url|copyright|news|service|initially|vol|issue|filed|ms|virginia|alexandria|last updated|database|startofarticle|af|rights|october|reserved|september|research articles|proquest document id|",
  "classification|https|--|people|alt|article|page|based|language|english|length|words|publication|type|morg|york|times|'new york times'|publication   info|illustration|date|caption|[0-9.]|new york times|identifier/keyword|twitter\\.|rauchway|keynes's|_ftn|enwikipediaorg|",
  "wwwnytimescom|wwwoenbat|wwwpresidencyucsbedu|wwwalt|wwwthemoneyillusioncom|aaa|predated|a_woman_to_reckon_with_the_vision_and_legacy_of_fran|ab_se|",
  "jcr:fec|ac|___________________|\\bwww\\b|[_]+",
  sep = ""
)
# Process bigrams
bigrams <- articles_df %>% 
  select(sentence) %>% 
  mutate(
    sentence = str_squish(sentence),                      # Remove extra spaces
    sentence = tolower(sentence),                         # Convert to lowercase
    sentence = str_replace_all(sentence, remove_pattern, ""), # Remove unwanted terms
    sentence = str_replace_all(sentence, "- ", ""),       # Remove trailing hyphens
    sentence = str_replace_all(sentence, "\\b[a-zA-Z]\\b", "") # Remove single characters
  ) %>% 
  unnest_tokens(bigram, sentence, token = "ngrams", n = 2) %>% 
  separate(bigram, c("word1", "word2"), sep = " ") %>% 
  filter(!word1 %in% stop_words$word) %>%                 # Filter out stop words
  filter(!word2 %in% stop_words$word) %>% 
  filter(!word1 %in% remove_pattern) %>% 
  count(word1, word2, sort = TRUE) %>% 
  filter(!is.na(word1) & !is.na(word2))                   # Filter out NAs

bigrams
```

## top 20 bigrams
```{r}
top_20_bigrams <- bigrams |> 
   top_n(20) |> 
  mutate(bigram = paste(word1, " ", word2)) |> 
  select(bigram, n)
```
## Visualization of bigrams  

```{r}
ggplot(top_20_bigrams, aes(x = reorder(bigram, n), y = n, fill=n)) +
  geom_bar(stat = "identity") +
  theme(legend.position = "none") +
  coord_flip() +  
  labs(title = "Top Two-Word phrases in FramingAI articles",
       caption = "n=500 articles. Graphic by Taufiq Ahmad. 11-24-2024",
       x = "Phrase",
       y = "Count of terms")
```


## Sentiment Analysis

```{r}
library(textdata)
library(quanteda)
```

#Tokenize text

```{r}
text_tokenized <- articles_df %>% 
  select(sentence) %>% 
  unnest_tokens(word, sentence)
```

#Filter tokenized text
```{r}
text_tokenized <- articles_df %>% 
  select(sentence) %>% 
  mutate(sentence = str_replace_all(sentence, "- ", "")) %>% 
  unnest_tokens(word, sentence) %>% 
  filter(!word %in% stop_words$word) %>% 
  filter(word != "stories_corpus") %>%
  filter(!grepl('[0-9]', word))
```


## word count 
```{r}
text_word_ct <- text_tokenized %>%
  count(word, sort=TRUE)
text_word_ct
```

## Loading NRC lexicon
```{r}
nrc_sentiments <- get_sentiments("nrc")

nrc_sentiments %>% count(sentiment)

nrc_sentiments %>% 
  group_by(word) %>% 
  count() %>% 
  arrange(desc(n)) %>% 
  distinct()
```

## Counting Overall Sentiment with NRC
```{r}
sentiments_all <- text_tokenized %>%
  inner_join(nrc_sentiments) 

sentiments_all %>% 
  group_by(word) %>% 
    count(sentiment) %>% 
  arrange(desc(n))
```

```{r}
sentiments_all <- text_tokenized %>%
  inner_join(nrc_sentiments) %>%
  count(sentiment, sort = TRUE) %>% 
  mutate(pct_total =round(n/sum(n), digits=2))

sentiments_all
```

## Visualizing the sentimental Analysis 

```{r}
nrc_plot <- sentiments_all %>% 
  ggplot(aes(x = reorder(sentiment, n), y = n, fill = sentiment)) + 
  geom_bar(stat = "identity", position = "dodge", width = 0.7) +  
  geom_text(aes(label = n), hjust = 1.2, size = 4, color = "white") +  
  labs(
    title = "Sentiment Analysis of Press Releases on AI and Disaster",
    subtitle = "NRC Sentiment Analysis Breakdown",
    caption = "Graphic by Taufiq Ahmad, Dec 1, 2024",
    x = "Sentiment",
    y = "Sentiment Score"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(face = "bold", size = 12, hjust = 0.5),  # Center and bold title
    plot.subtitle = element_text(size = 12, hjust = 0.5),  # Center subtitle
    plot.caption = element_text(hjust = 0, size = 10, face = "italic"),
    axis.text.x = element_text(size = 10, color = "grey40"),
    axis.text.y = element_text(size = 12, color = "grey40"),
    panel.grid.major.x = element_line(color = "grey90", linetype = "dotted"),  # Dotted grid lines
    panel.grid.major.y = element_blank(),  # Remove unnecessary grid lines
    legend.position = "none"  # Hide legend since colors are self-explanatory
  ) +
  scale_fill_manual(values = c(
    "positive" = "#1f77b4",   # Blue
    "negative" = "#d62728",   # Red
    "trust" = "#2ca02c",      # Green
    "fear" = "#9467bd",       # Purple
    "anticipation" = "#ff7f0e", # Orange
    "anger" = "#e377c2"       # Pink
  )) +  # Vibrant colors for each sentiment
  coord_flip()  # Flip for better readability

# Print the enhanced plot
print(nrc_plot)


```


## Checking the top words in some of the sentiments

## Positive
```{r}
nrc_positive <- nrc_sentiments %>%
  filter(sentiment == "positive")
FramingAI_positive <- text_tokenized %>%
  inner_join(nrc_positive) %>%
  count(word, sort = TRUE)
FramingAI_positive
```

## Trust
```{r}
#Trust
nrc_trust <- nrc_sentiments %>%
  filter(sentiment == "trust")
FramingAI_trust <- text_tokenized %>%
  inner_join(nrc_trust) %>%
  count(word, sort = TRUE)
FramingAI_trust
```


## Negative
```{r}
nrc_negative <- nrc_sentiments %>%
  filter(sentiment == "negative")
FramingAI_negative <- text_tokenized %>%
  inner_join(nrc_negative) %>%
  count(word, sort = TRUE)
FramingAI_negative
```


## Fear
```{r}
nrc_fear <- nrc_sentiments %>%
  filter(sentiment == "fear")
FramingAI_fear <- text_tokenized %>%
  inner_join(nrc_fear) %>%
  count(word, sort = TRUE)
FramingAI_fear
```


## Anticipation
```{r}
nrc_anticipation <- nrc_sentiments %>%
  filter(sentiment == "anticipation")
FramingAI_anticipation <- text_tokenized %>%
  inner_join(nrc_anticipation) %>%
  count(word, sort = TRUE)
FramingAI_anticipation
```

## Anger
```{r}
nrc_anger <- nrc_sentiments %>%
  filter(sentiment == "anger")
FramingAI_anger <- text_tokenized %>%
  inner_join(nrc_anger) %>%
  count(word, sort = TRUE)
FramingAI_anger
```

##combimation of All Sentiments 

```{r include=FALSE}

# Defining sentiments to analyze
sentiments <- c("positive", "trust", "negative", "fear", "anticipation", "anger")

# Process each sentiment and combine results into a single table
final_table <- lapply(sentiments, function(sentiment) {
  nrc_sentiments %>%
    filter(sentiment == !!sentiment) %>%
    inner_join(text_tokenized, by = "word") %>%
    count(word, sort = TRUE) %>%
    mutate(sentiment = sentiment)
}) %>%
  bind_rows() %>%
  pivot_wider(names_from = sentiment, values_from = n, values_fill = 0)

# View final table
print(final_table)

```

#Import the excel file
```{r include=FALSE}
library(tidyverse)
AI_disaster  <- rio::import("../data/AI_disaster. R.XLSX") %>%
  janitor::clean_names()
head(AI_disaster)
```


## visualization to show the distribution of the data over time

```{r}
library(tidyverse)
library(janitor)
library(lubridate)

# Clean and preprocess the data
AI_ggplot <- AI_disaster |> 
  janitor::clean_names() |> 
  mutate(published_date_bak = published_date) |> 
  separate(published_date, into = c("date", "year_day"), sep = ", ", extra = "merge", fill = "right") |> 
  mutate(date = as.Date(date, format = "%B %d")) |> # Convert to proper date format
  mutate(week = floor_date(date, unit = "week", week_start = 1)) |> # Group by week (starting on Monday)
  group_by(week) |> 
  count(week)

# Plotting the data
ggplot(AI_ggplot, aes(x = week, y = n)) +
  geom_line(color = "blue", size = 1) +
  geom_point(color = "red", size = 2) +
  scale_x_date(date_labels = "%b %d, %Y", date_breaks = "1 week") + # Show labels for every week
  labs(
    title = "Count of Press Releases Over Time (Weekly)",
    x = "Published Week",
    y = "Number of Press Releases"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.grid.major = element_line(size = 0.5, color = "gray"),
    panel.grid.minor = element_blank()
  )


```

#Where most Press Release published 
```{r include=FALSE}
pr_published_by <- AI_disaster %>%
  count(publication_4) %>%  
  group_by(publication_4) %>%  
  summarise(pr_published_by = sum(n)) %>%  
  arrange(desc(pr_published_by)) %>% 
 head(10)
```


## Visualize of NewsWires and Publishers 
```{r}

library(ggplot2)
library(ggthemes) # For additional themes

# for a bar chart
ggplot(pr_published_by, aes(x = reorder(publication_4, -pr_published_by), y = pr_published_by, fill = pr_published_by)) +
  geom_bar(stat = "identity", show.legend = FALSE) +
  geom_text(aes(label = pr_published_by), vjust = -0.5, size = 4, color = "black") +
  scale_fill_gradient(low = "lightblue", high = "darkblue") +
  theme_minimal(base_size = 12) +
  labs(
    title = "Top 10 Publications on AI and Disaster",
    subtitle = "Number of press releases published by each publication",
    x = "Publication",
    y = "Count of Published PRs"
  ) +
  theme(
    plot.title = element_text(face = "bold", size = 15, hjust = 0.5),
    plot.subtitle = element_text(size = 12, hjust = 0.5),
    axis.text.x = element_text(angle = 30, hjust = 1, size = 9),
    panel.grid.major = element_line(color = "grey80", linetype = "dashed")
  )

```

## topic modeling

```{r include=FALSE}
#install.packages("here")
#install.packages("tidytext")
#install.packages("quanteda")
#install.packages("tm")
#install.packages("topicmodels")
#install.packages("reshape2")
#install.packages("ggplot2")
#install.packages("wordcloud")
#install.packages("pals")
#install.packages("SnowballC")
#install.packages("lda")
#install.packages("ldatuning")
#install.packages("kableExtra")
#install.packages("DT")
#install.packages("flextable")
#install.packages("remotes")
#remotes::install_github("rlesur/klippy")
#install.packages("rio")
#install.packages("readtext")
#install.packages("formattable")
```

#Loading relevant libraries and packages for topic modelling

```{r include=FALSE}
# set options
options(stringsAsFactors = F)         # no automatic data transformation
options("scipen" = 100, "digits" = 4) # suppress math annotation
# load packages
here::here()
library(tidyverse)
library(tidytext)
library(rio)
library(readtext)
#topic modeling
library(quanteda)
library(tm)
library(topicmodels)
library(lda)
library(ldatuning)
# from tutorial packages
library(DT)
library(knitr)
library(kableExtra)
library(reshape2)
library(ggplot2)
library(wordcloud)
library(pals)
library(SnowballC)
library(flextable)
```

### Import Data and process into corpus

```{r}
topic_data <- articles_df %>%
  select(filename, sentence) %>%
  as.data.frame() %>%
  rename(doc_id = filename, text= sentence)

# load stopwords
english_stopwords <- readLines("https://slcladal.github.io/resources/stopwords_en.txt", encoding = "UTF-8")
# create corpus object
corpus <- Corpus(DataframeSource(topic_data))
# Preprocessing chain
processedCorpus <- tm_map(corpus, content_transformer(tolower))
processedCorpus <- tm_map(processedCorpus, removeWords, english_stopwords)
processedCorpus <- tm_map(processedCorpus, removePunctuation, preserve_intra_word_dashes = TRUE)
processedCorpus <- tm_map(processedCorpus, removeNumbers)
processedCorpus <- tm_map(processedCorpus, stemDocument, language = "en")
processedCorpus <- tm_map(processedCorpus, stripWhitespace)
```


```{r tm3a}
#DTM: rows correspond to the documents in the corpus. Columns correspond to the terms in the documents. Cells correspond to the weights of the terms. (Girder)
# compute document term matrix with terms >= minimumFrequency
minimumFrequency <- 5
DTM <- DocumentTermMatrix(processedCorpus, control = list(bounds = list(global = c(minimumFrequency, Inf))))
# have a look at the number of documents and terms in the matrix
dim(DTM)
# due to vocabulary pruning, we have empty rows in our DTM
# LDA does not like this. So we remove those docs from the
# DTM and the metadata
sel_idx <- slam::row_sums(DTM) > 0
DTM <- DTM[sel_idx, ]
topic_data <- topic_data[sel_idx, ]
#5 term minimum[1] 1387 3019
#5 term minimum[1] 308597 10339

```

```{r tm12}
# number of topics
# K <- 20
K <- 6
# set random number generator seed
set.seed(9161)
#Latent Dirichlet Allocation, LDA
topicModel2 <- LDA(DTM, K, method="Gibbs", control=list(iter = 1000, verbose = 25, alpha = 0.2))
tmResult <- posterior(topicModel2)
theta <- tmResult$topics
beta <- tmResult$terms
topicNames <- apply(terms(topicModel2, 10), 2, paste, collapse = " ")  # reset topicnames

```

### Extracting and visualizing the topics

```{r}
# Step 1: Check dimensions
n_theta <- nrow(theta)
n_topicdata<- length(topic_data)

cat("Number of rows in theta: ", n_theta, "\n")
cat("Number of documents in textdata: ", n_topicdata, "\n")

# Check if textdata contains all the documents in theta
common_ids <- intersect(rownames(theta), topic_data$doc_id) # Assuming textdata has a 'doc_id' column

# Filter textdata to include only the documents present in theta
topicdata_filtered <- topic_data[topic_data$doc_id %in% common_ids, ]

# Check dimensions after filtering
n_topicdata_filtered <- nrow(topicdata_filtered)
cat("Number of documents in filtered textdata: ", n_topicdata_filtered, "\n")


# Align rownames of theta with filtered textdata
theta_aligned <- theta[rownames(theta) %in% topicdata_filtered$doc_id, ]

# Step 2: Combine data
full_data <- data.frame(theta_aligned, decade = topicdata_filtered)

# get mean topic proportions per decade
# topic_proportion_per_decade <- aggregate(theta, by = list(decade = textdata$decade), mean)
# set topic names to aggregated columns
colnames(full_data)[2:(K+1)] <- topicNames
# reshape data frame
vizDataFrame <- melt(full_data)
   
#Examine topic names
#enframe(): Converts a named list into a dataframe.
topics <- enframe(topicNames, name = "number", value = "text") %>%
  unnest(cols = c(text))
 
topics
```


## EXTRACTED TOPICS 

1. program health committe research depart fund agenc univers word educ
2. presid trump peopl nation hous state american jean-pierr elect secretari
3. develop countri support china global cooper climat intern region secur
4. servic news oper net million result quarter financi incom year
5. data technolog solut market manag servic innov custom busi cloud





## Topic 1:
Words: program, health, committe, research, depart, fund, agenc, univers, word, educ

**Assessment: This cluster is indicative of Health and Education Programs within governmental and academic institutions. Words like "committee," "department," "fund," and "agency" point to structured organizational efforts, while "university" and "education" emphasize the academic involvement.

**Theme:
Health and Education Research Programs in Government and Academia

**Relevance to Project:
Health and education sectors often play crucial roles in disaster management. Analyzing how AI is framed within these programs can reveal interdisciplinary approaches and the integration of AI in public health and educational responses to disasters.

## Topic 2:
Words: presid, trump, peopl, nation, hous, state, american, jean-pierr, elect, secretari

**Assessment: This cluster revolves around Political Leadership and Governance in the United States. The inclusion of "Trump" and "president" highlights discussions related to specific political figures and their administrations. Words like "nation," "house," "state," and "secretary" indicate governance structures and political offices.

**Theme:
US Political Leadership and Governance

**Relevance to Project:
Political leadership significantly influences disaster response policies and the adoption of AI technologies. Examining this theme can uncover how political narratives and leadership styles shape the framing of AI in disaster management communications.

## Topic 3:
Words: develop, countri, support, china, global, cooper, climat, intern, region, secur

**Assessment: This cluster pertains to Global Development and International Cooperation, with a focus on Climate and Security Issues. The presence of "China" suggests discussions around international relations, while "climate" and "security" indicate environmental and geopolitical concerns.

**Theme:
Global Development, Climate Cooperation, and International Security

**Relevance to Project:
AI's role in addressing global challenges like climate change and international security is pivotal in disaster management. This theme can provide insights into how organizations frame AI as a tool for fostering international cooperation and enhancing global disaster response capabilities.

## Topic 4:
Words: servic, news, oper, net, million, result, quarter, financi, incom, year

**Assessment: This cluster focuses on Financial Performance and Operations within the Service and News Sectors. Words like "result," "quarter," "finance," "income," and "year" are indicative of financial reporting and business performance metrics.

**Theme:
Financial Performance and Operations of Service and News Sectors

**Relevance to Project:
Financial stability and operational efficiency are critical for organizations involved in disaster management. Understanding how AI-related financial results and operational successes are communicated can shed light on the economic framing of AI investments in disaster response.

## Topic 5:
Words: data, technolog, solut, market, manag, servic, innov, custom, busi, cloud

**Assessment: This cluster is centered around Data Technology Solutions and Cloud-based Business Services. Terms like "data," "technology," "solutions," "market," "management," "service," "innovation," "custom," "business," and "cloud" highlight the focus on technological advancements and business innovations.

**Theme:
Data Technology Solutions and Cloud-based Business Services

**Relevance to Project:
AI heavily relies on data and cloud technologies for effective disaster management. This theme is directly relevant as it encompasses the technological infrastructure and innovative solutions that organizations leverage, which are likely emphasized in their press releases regarding disaster response.


## Implications for Your Project:

#Diverse Organizational Focus: The identified themes suggest that AI in disaster management is framed across various organizational domains, including research institutions, government agencies, political entities, global cooperatives, financial sectors, and technology companies.

#Interdisciplinary Integration: AI is positioned as a multifaceted tool that intersects with health, education, political governance, global security, financial operations, and technological innovation. This highlights the interdisciplinary nature of AI applications in disaster management.

#Ethical and Risk Considerations: Themes related to governance, international cooperation, and financial operations may incorporate discussions on the ethical implications and risks of AI deployment, aligning with your research objectives.

#Strategic Communication: Understanding these themes can aid in analyzing the strategic narratives organizations use to communicate their AI initiatives, emphasizing benefits, addressing concerns, and positioning themselves within broader socio-political and economic contexts.



#Source of data compiled in your GitHub repository

I am sharing here the source of data that is available at GitHub with new repository named "FramingAI".

Reposotry : https://github.com/Taufiqahmad92/FramingAI
Data : https://github.com/Taufiqahmad92/FramingAI/tree/main/Data
