---
title: 'Homework: Summary of final project'
author: "Taufiq"
date: "2024-11-16"
output: html_document
---

#In this R Markdown document, I am providing a summary of your final project.

here you can find the detial of the data on this repository
#https://github.com/Taufiqahmad92/FramingAI

#to use the data and execute basic topic modeling with LADAL Method, I may need these packages and relevent libraries 

```{r echo= T, results = 'hide', warning=F, error=F, message=F}
library(tidyverse)
library(pdftools)
library(tidyverse)
library(textdata)
library(tidytext)
library(quanteda)
library(rio)
library(janitor)
library(rio)
library(dplyr)
library(stringr)
library(readr)
here::here()
#topic modeling
library(tm)
library(topicmodels)
library(lda)
library(ldatuning)
# from tutorial packages
library(DT)
library(knitr) 
library(kableExtra) 
library(reshape2)
library(ggplot2)
library(wordcloud)
library(pals)
library(SnowballC)
library(flextable)
```

#I am Loading the data here from the folder, while reading the files, combining the text, spliting into the document. 

```{r}
#reading PDF file and converting it into text. 
text <- pdf_text("./FramingAI_taufiq.PDF")
writeLines(text, "./FramingAI_taufiq.text")
file_path <- "./FramingAI_taufiq.text"
text_data <- readLines(file_path)
text_combined <- paste(text_data, collapse = "\n")
documents <- strsplit(text_combined, "End of Document")[[1]]
output_dir <- "./extracted"
for (i in seq_along(documents)) {
  output_file <- file.path(output_dir, paste0("FramingAI_extracted", i, ".txt"))
  writeLines(documents[[i]], output_file) 
}
cat("Files created:", length(documents), "\n")
FramingAI_index <- read_lines("./extracted/FramingAI_extracted1.txt")
extracted_lines <-FramingAI_index[16:2360]
cat(head(extracted_lines, 20), sep = "\n")
extracted_lines <- extracted_lines |> 
  as.data.frame() 
```

## Build a final dataframe index

```{r}

cleaned_data <- extracted_lines |>
  mutate(
    trimmed_line = str_trim(extracted_lines),  
    is_title = str_detect(trimmed_line, "^\\d+\\. "),  

    # Detect dates (e.g., "Aug 14, 2024")
    is_date = str_detect(trimmed_line, "\\b\\w{3} \\d{1,2}, \\d{4}\\b")
  )

# Shifting dates to align with corresponding titles
aligned_data <- cleaned_data |>
  mutate(
    date = ifelse(lead(is_date, 1), lead(trimmed_line, 1), NA_character_)  # Shift date to title's row
  ) |>
  filter(is_title) |>
  select(trimmed_line, date)  # Keep only the relevant columns

# Step 3: Rename columns for clarity
final_data <- aligned_data |>
  rename(
    title = trimmed_line,
    date = date
  )

# Date and Publication in separate columns, and formatted
final_data <- separate(data = final_data, col = date, into = c("date2", "publication"), sep = "  ", extra = "merge", fill = "right")


#Step 5: Format date, clean headline
final_data <- final_data |> 
  mutate(date = as.Date(date2,format = "%b %d, %Y")) |> 
  mutate(title =str_remove(title, "^\\d+\\. ")) |> 
  subset(select = -(date2)) |> 
  mutate(index = row_number()) |> 
  select(index, date, title, publication)

write_csv(final_data, "./final_data.csv")
```

#Using code, describe the number of rows and columns of the dataset
```{r}
ncol(final_data)
```

```{r}
nrow(final_data)
```


#Spell out your content analysis plan, including preliminary work on a code book

#Objective of the Project: 
  Analyze how U.S. organizations frame AI in press releases concerning disaster         response and management.

#Research Questions:
  1. How is AI framed in organizational press releases related to disaster management?
  2. What themes and narratives dominate discussions of AI in the context of natural        disasters and crises?
  3. What potential risks and ethical concerns regarding AI usage are highlighted in        these communications?
  
#Data collected:
      Data collected using Nexis Uni, spanning press releases from Nov. 1, 2023, to         Nov.1, 2024. Press releases that explicitly mention 'Artificial Intelligence' or       'AI' in conjunction with disasters, emergencies, or crisis management.

#Preliminary work on a code book is - In the Codebook Structure, I would define; 

Code Name - Definition	- Examples -	Coding Rules

#few tentative Code Names
AI Framing
Ethical Concerns
Misinformation Risks
Public Trust
AI Benefits
AI Limitations
Disaster Types
Organizational Strategies


#Provide a sample of the data and some descriptive statistics.

Total Press Releases:       	8,00
Time Period Covered:        	Nov. 1, 2023 – Nov. 1, 2024
Average Releases Per Month: 	125
Top Mentioned Keywords:       "Artificial Intelligence," "AI," "Disaster"
Dominant headlines of the press release:   Ethical Concerns, Public Trust, Misinformation, AI Benefits, AI Limitations
Most Active Month:	July 2024
Least Active Month:	February 2024
Regional Focus:	United States
Organizations Highlighted:	FEMA, Homeland Security, Tech Companies, NGOs



#Remember to create a separate folder for the entire assignment. Compress or "zip" the folder, push it to your github and hand in a link to that zip file.


#Create ggplot chart showing the distribution of the data over time


```{r}
library(readxl)
data <- read_excel("./AI_disaster. R.XLSX")

head(data)

```

#I am presenting ggplot from one month data. 

```{r}
library(ggplot2)

# Plotting the data
ggplot(data, aes(x = `Published date`, y = `Word count`)) +
  geom_line(color = "blue", size = 1) +
  geom_point(color = "red", size = 2) +
  labs(
    title = "Count of Press Releases Over Time",
    x = "Published Date",
    y = "Number of Press Releases"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```




#Render into an HTML page and post this to the web


# Specify a sheet name or index (optional)
